Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-10 csf-2017/paper.tex
minor

For reasons of space, some details and all proofs have been omitted;
please refer to the technical appendix~\cite{} for those.

@@

\caption{Permission-based conditions}
\label{fig:perm-conds}
\end{figure}
\clearpage
}
%subsection introduction
The logical relation defines semantically what it means to be
capability safe. In large parts, capability safety is defined by
when a capability safely can be given to an untrusted piece of
code. In the following paragraphs, we will go through the definitions
of the logical relation and provide an intuition why they define
capability safety.
The definition of the logical relation is found in
\figurename~\ref{fig:logrel}, \figurename~\ref{fig:standard-regions},
and \figurename~\ref{fig:perm-conds}. Some definitions are omitted and
explained when needed. The precise definitions can be found in the
technical report.\todo[inline]{add reference to technical report}

@@

\lars{don't know if we need the following paragraph:}
(Even though 
Hur and Dreyer~\cite{Hur:2011:KLR:1926385.1926402} also
considered a logical
relation involving an assembly language, they still used
biorthogonal closure but that was because their logical relation
was a relation between a high-level language and an assembly
language,  and thus the assembly language in the relation essentially
inherited structure from the high-level language.)

\section{Examples}
In this section, we display how capability safety allows us to prove
local state encapsulation and control-flow integrity properties. For
presentation purposes, we do not formally state the lemmas we
prove. The interested reader can find all the technical details in the
techincal report.

>>>>

For reasons of space, some details and all proofs have been omitted;
please refer to the technical appendix~\cite{XXX} for those.

@@

\caption{Permission-based conditions}
\label{fig:perm-conds}
\end{figure}
\clearpage
}
%subsection introduction
The logical relation defines semantically what it means to be
capability safe. In large parts, capability safety is defined by
when a capability safely can be given to an untrusted piece of
code. In the following paragraphs, we will go through the definitions
of the logical relation and provide an intuition why they define
capability safety.
The definition of the logical relation is found in
\figurename~\ref{fig:logrel}, \figurename~\ref{fig:standard-regions},
and \figurename~\ref{fig:perm-conds}. Some definitions are omitted and
explained when needed. The precise definitions can be found in the
technical report~\cite{XXX}.

@@

\lars{don't know yet whether we need something like the following paragraph:}
Even though 
Hur and Dreyer~\cite{Hur:2011:KLR:1926385.1926402} also
considered a logical
relation involving an assembly language, they still used
biorthogonal closure but that was because their logical relation
was a relation between a high-level language and an assembly
language,  and thus the assembly language in the relation essentially
inherited structure from the high-level language.

\section{Examples}
In this section, we display how capability safety allows us to prove
local state encapsulation and control-flow integrity properties. For
presentation purposes, we do not formally state the lemmas we
prove. 
\lars{I think it would be good if we can state one of them,
  possibly in shortened form, just to make it clear that something is
  actually stated and proved formally, and make a link to the LR}
The interested reader can find all the technical details in the
techincal report.
